---
title: "Activity #2"
---

Use **[ellmer](https://ellmer.tidyverse.org)** to interact with the an LLM (Anthropic, in this case) to generate feedback.

## Tooling

```{r}
#| label: source-prompt-fn
#| include: false
source("prompt.R")
```

`prompt.R`:

```{r}
#| echo: false
prompt
```

**Note:** The system prompt points to a file that has the contents of the [pipes chapter](https://style.tidyverse.org/pipes.html) of the Tidyverse style guide.

## Example: Tidying

Below is a question on tidying.

::: question
{{< include questions/tidy-country-inflation-pivot-longer/activity-2-tidy-country-inflation-pivot-longer-Q.qmd >}}
:::

<br>

```{r}
#| label: tidying-text
#| code-fold: true
#| code-summary: Code for constructing function inputs
question <- read_lines("questions/tidy-country-inflation-pivot-longer/tidy-country-inflation-pivot-longer-Q.qmd") |>
  glue_collapse() |>
  str_remove("---.*?---")

rubric <- read_lines("questions/tidy-country-inflation-pivot-longer/tidy-country-inflation-pivot-longer-R.qmd") |>
  glue_collapse() |>
  str_remove("---.*?---")

rubric_detailed <- read_lines("questions/tidy-country-inflation-pivot-longer/tidy-country-inflation-pivot-longer-RD.qmd") |>
  glue_collapse() |>
  str_remove("---.*?---")

bad_answer <- read_lines("questions/tidy-country-inflation-pivot-longer/tidy-country-inflation-pivot-longer-sample-answer-bad.qmd") |>
  glue_collapse() |>
  str_remove("---.*?---")

good_answer <- read_lines("questions/tidy-country-inflation-pivot-longer/tidy-country-inflation-pivot-longer-sample-answer-good.qmd") |>
  glue_collapse() |>
  str_remove("---.*?---")
```

::: {.panel-tabset}

### Bad

Below is what we might consider a bad answer to this question.

::: answer
{{< include questions/tidy-country-inflation-pivot-longer/activity-1-tidy-country-inflation-pivot-longer-sample-answer-bad.qmd >}}
:::

Provide feedback to the answer above using the following rubric.

::: rubric
{{< include questions/tidy-country-inflation-pivot-longer/activity-1-tidy-country-inflation-pivot-longer-R.qmd >}}
:::

```{r}
#| label: tidying-bad-eval-1
prompt(
  question = question, 
  rubric = rubric,
  answer = bad_answer
)
```

### Bad, again

Provide feedback to the same answer from the previous tab.

```{r}
#| label: tidying-bad-eval-2
prompt(
  question = question, 
  rubric = rubric,
  answer = bad_answer
)
```

### Good

Below is what we might consider a good answer to this question.

::: answer
{{< include questions/tidy-country-inflation-pivot-longer/activity-1-tidy-country-inflation-pivot-longer-sample-answer-good.qmd >}}
:::

Provide feedback to the answer above.

```{r}
#| label: tidying-good-eval-1
prompt(
  question = question, 
  rubric = rubric,
  answer = good_answer
)
```

:::

## Example: Modeling

Below is a question on modeling:

{{< include questions/model-birth-simple-linear/activity-2-model-births-simple-linear-Q.qmd >}}

<br>

```{r}
#| label: modeling-text
#| code-fold: true
#| code-summary: Code for constructing function inputs
question <- read_lines("questions/model-birth-simple-linear/model-births-simple-linear-Q.qmd") |>
  glue_collapse() |>
  str_remove("---.*?---")

rubric <- read_lines("questions/model-birth-simple-linear/model-births-simple-linear-R.qmd") |>
  glue_collapse() |>
  str_remove("---.*?---")

rubric_detailed <- read_lines("questions/model-birth-simple-linear/model-births-simple-linear-RD.qmd") |>
  glue_collapse() |>
  str_remove("---.*?---")

bad_answer <- read_lines("questions/model-birth-simple-linear/model-births-simple-linear-sample-answer-bad.qmd") |>
  glue_collapse() |>
  str_remove("---.*?---")

good_answer <- read_lines("questions/model-birth-simple-linear/model-births-simple-linear-sample-answer-bad.qmd") |>
  glue_collapse() |>
  str_remove("---.*?---")
```

::: {.panel-tabset}

### Bad

Below is what we might consider a bad answer to this question.

{{< include questions/model-birth-simple-linear/activity-2-model-births-simple-linear-sample-answer-bad.qmd >}}

Provide feedback to the answer above using the following rubric.

{{< include questions/model-birth-simple-linear/activity-2-model-births-simple-linear-R.qmd >}}

```{r}
#| label: modeling-bad-eval-1
prompt(
  question = question, 
  rubric = rubric,
  answer = bad_answer
)
```

### Good

Below is what we might consider a good answer to this question.

{{< include questions/model-birth-simple-linear/activity-2-model-births-simple-linear-sample-answer-good.qmd >}}

Provide feedback to the answer above.

```{r}
#| label: modeling-good-eval-1
prompt(
  question = question, 
  rubric = rubric,
  answer = good_answer
)
```

### Good, again

Provide feedback to the same answer from the previous tab.

```{r}
#| label: modeling-good-eval-2
prompt(
  question = question, 
  rubric = rubric,
  answer = good_answer
)
```

:::
